Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-02 paper/paper.tex
A bit of writing and moving

@@

@@

\section{Relationship between non-induced and induced subgraph isomorphism}

The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.

\begin{proposition}\label{prop:comp}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P \hookrightarrow T$ if and only if both $i$ satisfies the definition of $P \rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$.
\end{proposition}

\begin{proof}
Follows directly from the definition of an induced subgraph isomorphism and the definition of the complement of a graph.  Could flesh this out if we need to fill up space and look cleverer??
\end{proof}

\begin{corollary}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P \lessind{k} T$ if and only if both $i$ satisfies the definition of $P \lessnonind{k} T$ and $\bar{P} \lessnonind{k} \bar{T}$.
\end{corollary}

Should we just give the corollary as the proof??

>>>>

The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$. The
following proposition follows directly from the definitions.

\begin{proposition}\label{prop:comp}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
\hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
of $\bar{P} \rightarrowtail \bar{T}$.
Similarly, $i$ satisfies the definition of $P
\lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
$\bar{P}
\lessnonind{k} \bar{T}$.
\end{proposition}

@@

For both subgraph isomorphism and maximum common subgraph, constraint-based models are the best
approach (although constraint programming toolkits are not used, to facilitate better memory layouts
and propagation queues). For both problems, we create a variable for each vertex in the pattern
graph (the smaller graph, in the case of maximum common subgraph), with domains ranging over the
vertices in the target graph (the larger graph). For maximum common subgraph, each domain is given
an additional $\bot$ value, meaning ``unmapped''.

We also have constraints for adjacency and non-adjacency. For the maximum common subgraph case,
$\bot$ is ignored.

All different.

For subgraph isomorphism, we can also do domain filtering at the top of search. We discuss this in
??. Additional constraints, discuss this in ??.

@@
